Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
added mention of Van de Sampel work; address issue #63

Author guidelines in F1000Research, APA authors, SSI `publish or be damned'
\cite{ssi-publish-or-be-damned} manifesto, workflow for publishing code using
GitHub and Zenodo \cite{github-citable-code-guide}.
\dmnote{There are many other journals publishing software descriptions, some even specialized in software, e.g. \href{http://www.openresearchcomputation.com}{Open Research Computation}.}

>>>>

Van de Sompel et al.~\cite{VandeSompel2004} argued for registration of all units of scholarly communication, including software.\niemnote{suggesting this reference go here}
Author guidelines in F1000Research, APA authors, SSI `publish or be damned'
\cite{ssi-publish-or-be-damned} manifesto, workflow for publishing code using
GitHub and Zenodo \cite{github-citable-code-guide}.
\dmnote{There are many other journals publishing software descriptions, some even specialized in software, e.g. \href{http://www.openresearchcomputation.com}{Open Research Computation}.}
